Molecular Analysis

### 2023-10-03 analysis/mol_analysis.Rmd
revise transmission chain plot

```{r}
# combine
descr <- pos_tot_pl + plot_spacer() + pos_cond_pl & theme(legend.position = "bottom", legend.key.height = unit(.1, "cm"),
                                          legend.key.width = unit(.3, "cm"))
descr <- descr + plot_layout(guides = "collect", widths = c(9.5, 1, 5.5), ncol = 2) 
descr <- descr + tnet_pl 
descr <- descr + plot_layout(nrow = 2, heights = c(4, 16), design = 'ABC
                             DDD')
save_plot(descr, pdf_file = "../results/mol-data/descriptives.pdf", eps_file = "../results/mol-data/descriptives.eps", h = 24, w = 16)
# saveRDS(pos_tot_pl + ggtitle(""), file = "../results/mol-data/descriptives-total.rds")
# saveRDS(pos_cond_pl + ggtitle(""), file = "../results/mol-data/descriptives-cond.rds")
# saveRDS(pos_week_pl + ggtitle(""), file = "../results/mol-data/descriptives-week.rds")
```

>>>>

```{r}
# combine
descr <- pos_tot_pl + plot_spacer() + pos_cond_pl & theme(legend.position = "bottom", legend.key.height = unit(.1, "cm"),
                                          legend.key.width = unit(.3, "cm"))
descr <- descr + plot_layout(guides = "collect", widths = c(9.5, 1, 5.5), ncol = 2) 
descr <- descr + tnet_pl 
descr <- descr + plot_layout(nrow = 2, heights = c(4, 16), design = 'ABC
                             DDD')
save_plot(descr, pdf_file = "../results/mol-data/descriptives.pdf", eps_file = "../results/mol-data/descriptives.eps", h = 22, w = 16)
# saveRDS(pos_tot_pl + ggtitle(""), file = "../results/mol-data/descriptives-total.rds")
# saveRDS(pos_cond_pl + ggtitle(""), file = "../results/mol-data/descriptives-cond.rds")
# saveRDS(pos_week_pl + ggtitle(""), file = "../results/mol-data/descriptives-week.rds")
```
